Outline

### 2023-06-06 manuscript/outline.Rmd
Adding outline back in for figure info

  - Clockplot and univariate statistics
    - Report proportions of MFs in each category?
    - Many "bad" still have strong biology trend, not a sufficient measure on its own
    - Missing out on some good peaks (far left clockplot)
    - Do the FDR corrected p-value comparisons with more/less peaks by threshold

  - PERMANOVA table
    - Better performance somehow with 90% threshold than manually labeled "good" peaks?
    - Emphasize the lack of power when all peaks are included in the analysis with 1% and 0% thresholds
  - Actual biology things
    - Most metabolites track with biomass
    - Surface-specific largely MAAs, some new?
    - Degradation products or bacterial things accumulating at depth?

@@

  - Fundamental tradeoff between GPF and FDR should be determined by the scientific question
  - FDR and GPF rates are very rarely reported but critically important to include
  - Full model and XCMS model are definitely overfit
    - Steep performance drop on new data
    - Disagreement based on training set
  - Only tested on HILIC data, expectations for RP columns
  - Using medians/means as summary statistics ignores differences between treatments (i.e. lots of blanks blows up the median): maybe better to use max/top3? Maybe better to implement independently for each sample class?
  - XCMS alone does not provide enough information to distinguish good peaks from bad with much confidence

@@

In a Bayesian framework, the base rate (likelihood of being a real peak) is critically important for any downstream analysis.

>>>>

  - Clockplot and univariate statistics
    - Report proportions of MFs in each category?
    - Big central thing where all the noise ended up
    - Many "bad" still have strong biology trend, not a sufficient measure on its own
    - Missing out on some good peaks (far left clockplot)
    - Do the FDR corrected p-value comparisons with more/less peaks by threshold
  - PERMANOVA table
    - Better performance somehow with 90% threshold than manually labeled "good" peaks?
    - Emphasize the lack of power when all peaks are included in the analysis with 1% and 0% thresholds
  - Actual biology things
    - Most metabolites track with biomass
    - Surface-specific largely MAAs, some new?
    - Degradation products or bacterial things accumulating at depth?

@@

See the actual manuscript

@@
